Output of the source is in discrete time and discrete valued.

\begin{definition}
    The output is a sequence of letters from an (finite) alphabet $\U$.
\end{definition}

We want to decompose the encoder into a source encoder and a channel encoder. So, the number of encoder is linear with respect of the the number of sources and channel and not quadratic.

The source encoder outputs a stream of bits and don't care of the channel and the channel encoder translate the input stream of bits without considering the kind of data.

We can use this architecture without loss of generality.

\bigskip

Source coding : Representation of information sources in bits.

\begin{example}
    $\U = \set{a,b,c,d}$
    \[
        \begin{aligned}
            a &\ra 0\\
            b &\ra 0\\
            c &\ra 0\\
            d &\ra 1
        \end{aligned}
        \qquad \text{bad, "singular"}            
    \]
\end{example}

A source code is a function
\[
    \C : \U \ra \set{0;1}^*
\]

\begin{definition}
    A code $\C$ is called singular  if
    \[
        \exists (u,v) \in \U^2, u \neq v \wedge \C(u) = \C(v)
    \]
\end{definition}

\begin{definition}
    A code $\C$ is called non singular (injective) if
    \[
        \forall (u,v) \in \U^2, u \neq v \Ra \C(u) \neq \C(v)
    \]
\end{definition}

\begin{example}
    \[
        \begin{aligned}
            a &\ra 0\\
            b &\ra 00\\
            c &\ra 1\\
            d &\ra 11
        \end{aligned}
        \qquad \text{still bad, "not uniquely decodable"}            
    \]
\end{example}

\begin{definition}
    Given a code $\C : \U \ra \set{0;1}^*$, define for $n\in\NN^*$
    \[
        \C^n : \U^n \ra \set{0;1}^*
    \]
    as
    \[
        \C^n(u_1\ldots u_n) = \C(u_1) \ldots \C(u_n)
    \]
    and
    \[
        \C^* : \U^* \ra \set{0;1}^*
    \]
    as
    \[
        \C^n(u_1\ldots u_k) = \C(u_1) \ldots \C(u_k)
    \]
\end{definition}

\begin{definition}
    A code $\C$ is said to be uniquely decodable if $\C^*$ is injective (non singular).
\end{definition}

We want our code to be uniquely decodable.

\begin{definition}
    A sequence $u_1\ldots u_m$ is a prefix of $v_1 \ldots v_n$ if $n\leqslant m$ and $\forall i\in\llbracket 1,m\rrbracket, u_i = v_i$.
\end{definition}

\begin{example}
    \[
        \begin{aligned}
            a &\ra 0\\
            b &\ra 10\\
            c &\ra 110\\
            d &\ra 111
        \end{aligned}       
    \]
    
    \[
        \underbrace{110}_{c}\underbrace{110}_{c}\underbrace{0}_{a}\underbrace{111}_{d}\underbrace{10}_{b} \underbrace{0}_{a}
    \]
\end{example}

\begin{definition}
    A code $\C$ is said to be prefix free if $\C(u)$ is not a prefix of $\C(v)$ for all $u\neq v$.
\end{definition}

\begin{theorem}
    A prefix free code is uniquely decodable.
\end{theorem}
\begin{proof}
    Suppose that $\C$ is prefix free but not uniquely decodable. So, there is  $u_1\ldots u_m$ and $v_1\ldots, v_n$ such that $u_1\ldots u_m \neq v_1\ldots, v_n$ and $\C(u_1) \ldots \C(u_m) = \C(v_1) \ldots \C(v_n)$.

    Without loss of generality, we can assume $u_1 \neq v_1$.
    
    Suppose $\C(u_1)$ is longer than $\C(v_1)$ $\Ra$ $\C(v_1)$ is a prefix of $\C(u_1)$: contradiction.
    
    In the other case, $\C(u_1)$ is a prefix of $\C(v_1)$: contradiction.
\end{proof}

\begin{example}
    \[
        \begin{aligned}
            a &\ra 0\\
            b &\ra 01\\
            c &\ra 011\\
            d &\ra 111
        \end{aligned}
        \qquad \text{not prefix free but still uniquely decodable}
    \]
    
    \[
        \underbrace{110}_{c}\underbrace{110}_{c}\underbrace{111}_{d}
    \]
\end{example}

Binary tree representation of source codes.

\begin{center}
	\Tree [.$\emptyset$ [.0 [.00 [000 ] [001 ] ] [.01 [010 ] [011 ] ] ] [.1 [.10 [100 ] [101 ] ] [.11 [110 ] [111 ] ] ] ]
\end{center}

\begin{center}
	\Tree [ [.$\C(b)$ [$\C(a)$ ] [$\C(c)$ ] ] [[ ] [[ ][ ] ] ] ]
	$\ra$ not prefix free.
\end{center}

\begin{center}
    \Tree [[[ ][$\C(a)$ ]][[$\C(b)$ ][[$\C(c)$ ][$\C(d)$ ] ] ] ]
    $\ra$ prefix free
\end{center}

\begin{remark}
    In the binary tree representation of a prefix tree code, all codewords are found on the leaves.
\end{remark}