Inspired by \textsc{Tunstall}, 

\begin{algorithm}
    \DontPrintSemicolon
    Set $\D=\U$\;
    \While{The text is not entirely coded}{
        Associate to each $w \in \D$ a $\ceil{\log\card\D}$-bit binary representation, based on dictionary order.\;
        Parse the next word $w$ from the source sequence using $\D$.\;
        Emit the binary representation of $w$.\;
        $\D \la \D\setminus\set{w} \cup \set{wu\vert u\in\U}$\;
    }
\end{algorithm}

\begin{example}
    $\U = \set{a,b,c}$, source = $bbaacbaa$.

    $\D = \set{\underset{\underset{00}{\downarrow}}{a},\underset{\underset{01}{\downarrow}}{b},\underset{\underset{10}{\downarrow}}{c}}$, source = $\textcolor{blue}{b}baacbaa$, output = \textcolor{blue}{01}.

    $\D = \set{\underset{\underset{000}{\downarrow}}{a},\underset{\underset{001}{\downarrow}}{ba},\underset{\underset{010}{\downarrow}}{bb},\underset{\underset{011}{\downarrow}}{bc},\underset{\underset{100}{\downarrow}}{c}}$ source = $\textcolor{blue}{ba}acbaa$, output = 01\textcolor{blue}{001}

    $\D = \set{\underset{\underset{000}{\downarrow}}{a},\underset{\underset{001}{\downarrow}}{baa},\underset{\underset{010}{\downarrow}}{bab},\underset{\underset{011}{\downarrow}}{bac},\underset{\underset{100}{\downarrow}}{bb},\underset{\underset{101}{\downarrow}}{bc},\underset{\underset{110}{\downarrow}}{c}}$ source = $\textcolor{blue}{a}cbaa$, output = 01001\textcolor{blue}{000}

    \bigskip    

    At the decoder side, we have $\U = \set{a,b,c}$ and the representation $\underbrace{01}_b\underbrace{001}_{ba}\underbrace{000}_{a}\ldots$
\end{example}

Analysis of the performance of L-Z.

We will show LZ perform well by showing that is is competitive vs a class of adversary.

The class we choose is the class of finite-state-automaton compressors.

We will define, given a finite state machine compressor, $E$, and a sequence $u_1u_2\ldots \in \U^\infty$, let
\[
    \rho(E,u_1u_2\ldots) = \limsup\limits_{n\to\infty} \frac{\text{\# of bits }E\text{ has produces upon reading }u_1u_2\ldots}{n}
\]
be the compressibility of $u_1u_2\ldots$ by the machine $E$.

\[
    \begin{aligned}
        \rho_{FSA}(u) &= \inf\limits_{E\text{ FSA}} \rho(E,u)\\
        &= \lim\limits_{s \to \infty}\min\limits_{\substack{E\text{ FSA}\\\text{with less that }n \text{ states}}} \rho(E,u)\\
    \end{aligned}
\]

Define also
\[
        \rho_{LZ}(u) = \limsup\limits_{n\to\infty} \frac{\text{\# of bits LZ has produced upon reading }u}{n}
\]
We sill show $\rho_{LZ}(u) = \rho_{FSA}(u)$.

\begin{definition}[Finite State Automaton]
    Cf. \textit{Introduction à la calculabilité}, \textsc{Chevalier} \footnote{\url{http://perso.ens-lyon.fr/marc.chevalier/Calculabilite/Calculabilite.pdf}} pp.273 sqq.
\end{definition}

We add an output function: $f:S\times \Sigma \to \set{0,1}^*$. Such an automaton output a binary word at each transition.

If you really want a figure, be my guest. I don't want to have to (be) fuck (by) Tikz one time more.

\begin{notation}
    We extend the transition function on $Q \times \Sigma^*$
    \[
        \delta(s, u_1\ldots u_k) = \delta(\ldots\delta(s, u_1),\ldots,u_k)
    \]
    
    Similarly, we extend the output function
    \[
        f(s,u_1\ldots u_k) = f(s,u_1) \Vert f(\delta(s, u_1), u_2\ldots u_k)    
    \]
\end{notation}

Assume further that every state $q$ is reachable from $s_0$.

Suppose we have an FSA, suppose it has a state $q$ and two sequences $u_1\ldots u_m$ and $v_1,\ldots,v_n$ such that
\[
    \begin{aligned}
        g(q, u_1\ldots u_m) &= g(q, v_1\ldots v_n)\\
        f(q, u_1\ldots u_m) &= f(q, v_1\ldots v_n)
    \end{aligned}
\]

\begin{theorem}
    The following two infinite sequences are indistinguishable at the output
    \begin{itemize}
        \item $p \Vert u_1 \ldots u_m \Vert s$
        \item $p \Vert v_1 \ldots v_n \Vert s$
    \end{itemize}
    where $p$ is a special string to take the machine from $q_0$ to $q$ and $s$ is any infinite sequence.
\end{theorem}

Such machine consequently is not legitimate (its output does not determine its input).

\begin{corollary}
    So a legitimate machine has to have the following property: for any $q\in Q$ and any $u_1\ldots u_m \neq v_1\ldots v_n$
    \[
            g(q,u_1\ldots u_m) = g(q,v_1\ldots v_m) \Ra f(q,u_1\ldots u_m) \neq f(q,v_1\ldots v_n)
    \]
\end{corollary}
such machines are called information-lossless.

Legitimate FSA are information lossless. But the reverse is not true.

We will use the information-lossless property of legitimate FSA to show that they can't emit too few bits. Consider a sequence $u_1\ldots u_n$ being fed to an IL machine.

Suppose we parse $u_1\ldots u_n$ into a sequence $w_1 \ldots w_k$ of distinct words ($w_i \neq w_j$ when $i\neq j$). Let $\W_{s,t} = \set{i \vert w_i \text{ finds the machine at state }s\text{, leaves the machine at state }t}$.

So $\brackets{1;k} = \bigcup\limits_{s,t} \W_{s,t}$ (disjoint union).

Let $Y_i \in \set{0,1}^*$ be the binary sequence emitted during the reading of $w_i$. Observe that if $i$ and $j$ are both in $\W_{st}$ then $Y_i \neq Y_j$. So if $\lvert \W_{s,t}\rvert = m$ then in the output produced by the machine we have $m$ distinct binary sequences.

\[
    \sum\limits_{i \in \W_{st}} \length{Y_i} \geqslant m\log\frac{m}{8}
\]


So the machine having read $u_1\ldots u_n$ ($=w_1\ldots w_k$) has produces $y_1\ldots y_k$ with $\length{y_1\ldots y_k} = \sum\limits_{k=1}^k \length{y_i} = \sum\limits_{s,t}\sum\limits_{i\in W_{s,t}} \length{y_i} \geqslant \sum\limits_{s,t} \card{\W_{s,t}} \log\frac{\card{\W_{s,t}}}{8}\geqslant k\log\frac{k}{8\card{Q}^2}$.


